---
title: "Business Intelligence Lab Submission Markdown"
author: "Team quatum"
date: "10/3/2023"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one student name, class group (just the letter; A, B, or C), and ID per line, e.g., 123456 - A - John Leposo; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                                                                                          |
|                                                   | 1.  134985 - Team Quatum - Ibrahim Mohamed                                                                                                                                             |
|                                                   |                                                                                                                                                                          |
|                                                   | 2.  122268 - Team Quatum - Lambert Othieno                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 3.  136018 - Team Quatum - Earl Wanjala                                                                                                                                              |
|                                                   |                                                                                                                                                                          |
|                                                   | 4.  134787 - Team Quatum - Edwin Onyango                                                                                                                                             |
|                                                   |                                                                                                                                                                          |
|                                                   | 5.  135590 - Team Quatum - Fareed Matovu   

|                                                   | 5.  131123 - Team Quatum - Alex Mwai                     |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | *\<Team Quatum \>*                                                                                                       |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                                                                                                  |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                                                                                                 |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                                                                                              |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                                                                                               |
+---------------------------------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

# Setup Chunk

We start by installing all the required packages

```{r Install Packages, echo=TRUE, message=FALSE, warning=FALSE}
## formatR - Required to format R code in the markdown ----
if (!is.element("formatR", installed.packages()[, 1])) {
  install.packages("formatR", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("formatR")


## readr - Load datasets from CSV files ----
if (!is.element("readr", installed.packages()[, 1])) {
  install.packages("readr", dependencies = TRUE,
                   repos="https://cloud.r-project.org")
}
require("readr")
```

------------------------------------------------------------------------

**Note:** the following "*KnitR*" options have been set as the defaults in this markdown:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, echo=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

------------------------------------------------------------------------

**Note:** the following "*R Markdown*" options have been set as the defaults in this markdown:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Loading the Student Performance Dataset

The 20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset is then loaded. The dataset and its metadata are available here: <https://drive.google.com/drive/folders/1-BGEhfOwquXF6KKXwcvrx7WuZXuqmW9q?usp=sharing>

```{r Load Dataset}
student_performance_dataset <-
  readr::read_csv(
                  "data/Performance Dataset CSV.csv", # nolint
                  col_types =
                  readr::cols(
                              class_group =
                              readr::col_factor(levels = c("A", "B", "C")),
                              gender = readr::col_factor(levels = c("1", "0")),
                              YOB = readr::col_date(format = "%Y"),
                              regret_choosing_bi =
                              readr::col_factor(levels = c("1", "0")),
                              drop_bi_now =
                              readr::col_factor(levels = c("1", "0")),
                              motivator =
                              readr::col_factor(levels = c("1", "0")),
                              read_content_before_lecture =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              anticipate_test_questions =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              answer_rhetorical_questions =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              find_terms_I_do_not_know =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              copy_new_terms_in_reading_notebook =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              take_quizzes_and_use_results =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              reorganise_course_outline =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              write_down_important_points =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              space_out_revision =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              studying_in_study_group =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              schedule_appointments =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              goal_oriented =
                              readr::col_factor(levels =
                                                c("1", "0")),
                              spaced_repetition =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              testing_and_active_recall =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              interleaving =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              categorizing =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              retrospective_timetable =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              cornell_notes =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4")),
                              sq3r = readr::col_factor(levels =
                                                       c("1", "2", "3", "4")),
                              commute = readr::col_factor(levels =
                                                          c("1", "2",
                                                            "3", "4")),
                              study_time = readr::col_factor(levels =
                                                             c("1", "2",
                                                               "3", "4")),
                              repeats_since_Y1 = readr::col_integer(),
                              paid_tuition = readr::col_factor(levels =
                                                               c("0", "1")),
                              free_tuition = readr::col_factor(levels =
                                                               c("0", "1")),
                              extra_curricular = readr::col_factor(levels =
                                                                   c("0", "1")),
                              sports_extra_curricular =
                              readr::col_factor(levels = c("0", "1")),
                              exercise_per_week = readr::col_factor(levels =
                                                                    c("0", "1",
                                                                      "2",
                                                                      "3")),
                              meditate = readr::col_factor(levels =
                                                           c("0", "1",
                                                             "2", "3")),
                              pray = readr::col_factor(levels =
                                                       c("0", "1",
                                                         "2", "3")),
                              internet = readr::col_factor(levels =
                                                           c("0", "1")),
                              laptop = readr::col_factor(levels = c("0", "1")),
                              family_relationships =
                              readr::col_factor(levels =
                                                c("1", "2", "3", "4", "5")),
                              friendships = readr::col_factor(levels =
                                                              c("1", "2", "3",
                                                                "4", "5")),
                              romantic_relationships =
                              readr::col_factor(levels =
                                                c("0", "1", "2", "3", "4")),
                              spiritual_wellnes =
                              readr::col_factor(levels = c("1", "2", "3",
                                                           "4", "5")),
                              financial_wellness =
                              readr::col_factor(levels = c("1", "2", "3",
                                                           "4", "5")),
                              health = readr::col_factor(levels = c("1", "2",
                                                                    "3", "4",
                                                                    "5")),
                              day_out = readr::col_factor(levels = c("0", "1",
                                                                     "2", "3")),
                              night_out = readr::col_factor(levels = c("0",
                                                                       "1", "2",
                                                                       "3")),
                              alcohol_or_narcotics =
                              readr::col_factor(levels = c("0", "1", "2", "3")),
                              mentor = readr::col_factor(levels = c("0", "1")),
                              mentor_meetings = readr::col_factor(levels =
                                                                  c("0", "1",
                                                                    "2", "3")),
                              `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                              readr::col_factor(levels = c("0", "1")),
                              GRADE = readr::col_factor(levels =
                                                        c("A", "B", "C", "D",
                                                          "E"))),
                  locale = readr::locale())
```

## Description of the Dataset

We then display the number of observations and number of variables. We have 101 observations and 100 variables to work with.

```{r Your Fourth Code Chunk}
dim(student_performance_dataset)
```

Next, we display the quartiles for each numeric variable[*... think of this process as **"storytelling using the data."** Tell us what is happening; tell us what you are discovering as you proceed with the markdown; walk us through your code step-by-step (a code walkthrough).*]{#highlight style="color: blue"}

```{r Your Fifth Code Chunk}
summary(student_performance_dataset)
```

# \<Rendering the .Rmd file in R Studio \>

Render the .Rmd (R markdown) file into its .md (markdown) version by using
knitR in RStudio.


```{r Your Sixth Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
if (!is.element("knitR", installed.packages()[, 1])) {
install.packages("knitR", dependencies = TRUE,
repos = "https://cloud.r-project.org")
}
require("knitR")

```

# \<Installing Pandoc\>

In this section we will install the pandoc package


```{r Your Seventh Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
if (!is.element("pandoc", installed.packages()[, 1])) {
install.packages("pandoc", dependencies = TRUE,
repos = "https://cloud.r-project.org")
}
require("pandoc")
```

## \<You Can Have Another Sub-Title Here if you wish\>

Describe the code chunk here.

```{r Your Eighth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
```

**etc.** as per the lab submission requirements. Be neat and communicate in a clear and logical manner.
